### 2019-04-08 README.Rmd

```{r install, eval = FALSE}
install.packages("BiocManager")

```

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions. Please do get in touch (preferable opening
a [github issue](https://github.com/lgatto/MSnbase/issues/)) to
discuss any suggestions. The
[`MSnbase` development vignette](http://lgatto.github.io/MSnbase/articles/MSnbase-development.html) gives
some background on the class infrastructure.

>>>>

```{r install, eval = FALSE}
install.packages("BiocManager")
BiocManager::install("MSnbase")
```

@@

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions. Please do get in touch (preferable opening
a [github issue](https://github.com/lgatto/MSnbase/issues/)) to
discuss any suggestions. The
[`MSnbase` development vignette](http://lgatto.github.io/MSnbase/articles/v05-MSnbase-development.html) gives
some background on the class infrastructure.
